On Secure Delegation of SampBQP with a Classical Client

### 2020-02-09 qpip.tex
Change autoref to cref

\begin{lemma}
	\label{ProtoGroundStateCheck}
	There is a $\QPIP_1$ protocol for \autoref{AlgGroundStateCheck}. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
\end{lemma}
\begin{prf}
	The prover simply sends the input qubit-by-qubit for the verifier to measure. It is clear that any attacks on this scheme trivially maps onto an attack on the original scheme.
\end{prf}

@@

\begin{protocol}{$\QPIP_1$ protocol for $\SampBQP$}
	\label{ProtoQPIP1}
	\begin{itemize}
		\item Let $\varepsilon>0$
		\item Let $m$ be large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
		\item Let $n$ be large enough so both
			$$P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]$$
			and
			$$P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]$$ are negligible in $\varepsilon$ by Chernoff bound
		\item Let $N$ be large enough so that $$\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}<\varepsilon$$
			where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$
	\end{itemize}
	\begin{enumerate}
		\item The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
		\item The verifier randomly picks $m$ copies for outputting and $n$ copies for checking
		\item Set counter $c=0$
		\item Set $y=\bot$
		\item For $i$ from $1$ to $N$:
		\begin{enumerate}
			\item If the $i$-th register is for checking:
			\begin{enumerate}
				\item The verifier runs \autoref{AlgGroundStateCheck} as described by \hyperref[ProtoGroundStateCheck]{Observation~\ref*{ProtoGroundStateCheck}}.
				\item If the test passes, increment counter $c$.
			\end{enumerate}
			\item If the register is for outputting:
			\begin{enumerate}
				\item The verifier measures the copy in standard basis
				\item If the measurement result of the clock register $\geq\frac{T}{2}$ and $y=\bot$, then update $y$ as the measurement result of the data register.
			\end{enumerate}
			\item Otherwise, just measure the entire register in standard basis and discard it.
		\end{enumerate}
		\item If $\frac{c}{n}\geq\frac{1}{2}-\varepsilon$:
		\begin{enumerate}
			\item If $y\ne\bot$ then output $y$
			\item Otherwise, reject.
		\end{enumerate}
		\item Otherwise, reject.
	\end{enumerate}
\end{protocol}

@@

	So we can apply \autoref{deFinetti}. $\exists\set{w_i, \rho_i}$ such that:
	$$\max_{\Lambda_i}\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+n}(\sigma'-\sum_i w_i\rho_i^{\otimes n+m})}=O(\varepsilon)$$

@@

	Let $p_i$ be the accept probability of at least $(\frac{1}{2}-\varepsilon)n$ copies from $\rho_i^{\otimes n}$ accept under \autoref{AlgGroundStateCheck}.
	So the accept chance of this prover is $\sum_j w_j p_j>\delta$
	By Bayes' theorem, conditioned on acceptance, the probability of $\tilde{\sigma}$ being $\rho_i^{\otimes n+m}$ is then $\frac{w_i p_i}{\sum_j w_j p_j}$.

@@

	So by Bayes' theorem, conditioned on acceptance, the probability of $\tilde{\sigma}$ being $\rho_i^{\otimes n+m}$ where $\rho_i$ has over probability $1-2\varepsilon$ to be accepted by \autoref{AlgGroundStateCheck} is overwhelming.

	Such $\rho_i$ is $O(\negl(\varepsilon))$-close to $\ket{\psi_{C'(x)}}$, by applying a Chernoff bound to \autoref{ThmXZCheck}.

>>>>

\begin{lemma}
	\label{ProtoGroundStateCheck}
	There is a $\QPIP_1$ protocol for \cref{AlgGroundStateCheck}. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
\end{lemma}
\begin{prf}
	The prover simply sends the input qubit-by-qubit for the verifier to measure. It is clear that any attacks on this scheme trivially maps onto an attack on the original scheme.
\end{prf}

@@

\begin{protocol}{$\QPIP_1$ protocol for $\SampBQP$}
	\label{ProtoQPIP1}
	\begin{itemize}
		\item Let $\varepsilon>0$
		\item Let $m$ be large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
		\item Let $n$ be large enough so both
			$$P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]$$
			and
			$$P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]$$ are negligible in $\varepsilon$ by Chernoff bound
		\item Let $N$ be large enough so that $$\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}<\varepsilon$$
			where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$
	\end{itemize}
	\begin{enumerate}
		\item The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
		\item The verifier randomly picks $m$ copies for outputting and $n$ copies for checking
		\item Set counter $c=0$
		\item Set $y=\bot$
		\item For $i$ from $1$ to $N$:
		\begin{enumerate}
			\item If the $i$-th register is for checking:
			\begin{enumerate}
				\item The verifier runs \cref{AlgGroundStateCheck} as described by \hyperref[ProtoGroundStateCheck]{Observation~\ref*{ProtoGroundStateCheck}}.
				\item If the test passes, increment counter $c$.
			\end{enumerate}
			\item If the register is for outputting:
			\begin{enumerate}
				\item The verifier measures the copy in standard basis
				\item If the measurement result of the clock register $\geq\frac{T}{2}$ and $y=\bot$, then update $y$ as the measurement result of the data register.
			\end{enumerate}
			\item Otherwise, just measure the entire register in standard basis and discard it.
		\end{enumerate}
		\item If $\frac{c}{n}\geq\frac{1}{2}-\varepsilon$:
		\begin{enumerate}
			\item If $y\ne\bot$ then output $y$
			\item Otherwise, reject.
		\end{enumerate}
		\item Otherwise, reject.
	\end{enumerate}
\end{protocol}

@@

	So we can apply \cref{deFinetti}. $\exists\set{w_i, \rho_i}$ such that:
	$$\max_{\Lambda_i}\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+n}(\sigma'-\sum_i w_i\rho_i^{\otimes n+m})}=O(\varepsilon)$$

@@

	Let $p_i$ be the accept probability of at least $(\frac{1}{2}-\varepsilon)n$ copies from $\rho_i^{\otimes n}$ accept under \cref{AlgGroundStateCheck}.
	So the accept chance of this prover is $\sum_j w_j p_j>\delta$
	By Bayes' theorem, conditioned on acceptance, the probability of $\tilde{\sigma}$ being $\rho_i^{\otimes n+m}$ is then $\frac{w_i p_i}{\sum_j w_j p_j}$.

@@

	So by Bayes' theorem, conditioned on acceptance, the probability of $\tilde{\sigma}$ being $\rho_i^{\otimes n+m}$ where $\rho_i$ has over probability $1-2\varepsilon$ to be accepted by \cref{AlgGroundStateCheck} is overwhelming.

	Such $\rho_i$ is $O(\negl(\varepsilon))$-close to $\ket{\psi_{C'(x)}}$, by applying a Chernoff bound to \cref{ThmXZCheck}.
